Visualizations for the manuscript

### 2022-06-23 metanalysis_visualization/manuscript_Figures.Rmd
close the gap in the ITS plots and format the top label with CI and without p-value

ci_boot <- bootstrapped_coefficients_all %>% 
  group_by(siteid, term) %>% 
  summarise("2.5%" = quantile(bootstrapped_slope_coefficient, 0.025), 
            "50%" = quantile(bootstrapped_slope_coefficient, 0.50), 
            "97.5%" = quantile(bootstrapped_slope_coefficient, 0.975)) %>% 
  mutate(ci = paste0("[95% CI ", as.character(round(`2.5%`, 2)), "–", as.character(round(`97.5%`, 2)), "]"))

@@

```{r}
pvalues_boot_complete <- pvalues_boot %>% 
  inner_join(ci_boot) %>% 
  inner_join(country_map) %>% 
  arrange(plotsLabel) %>% 
  mutate(string = paste0(observed_slope_coefficient, "% ", ci, " (p-value ", format.pval(pvalue, digits = 3, eps = 10**-2), ")")) %>% 
  select(plotsLabel, string) %>% 
  pivot_wider(names_from = term, values_from = string) %>% 
  select(plotsLabel, before_slope, during_slope, difference_slope) %>% 
  rename("Before pandemic trend [95% CI] (p-value)" = before_slope,
        "Since pandemic trend [95% CI] (p-value)" = during_slope,
        "Difference before/since pandemic trend [95% CI] (p-value)" = difference_slope)

@@

```{r}
ggplot(bootstrapped_fitted_all,
       aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_all,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = 6)+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  scale_colour_manual(values = cbPalette, labels = c("pre-pandemic", "pandemic"), name = "Period") +
  geom_label(data = plot_annotations_df_primary, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(
    #title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
    #subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 14),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        panel.grid.minor.x = element_blank(), 
        panel.grid.minor.y = element_blank(),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic"), 
        legend.position="bottom")

@@

bootstrapped_fitted_sex %>% 
  filter( sex == "female") %>%
  mutate(period = recode_factor(period, "before_pandemic" = "Before pandemic onset", "during_pandemic" = "Since pandemic onset")) %>% 
  ggplot(aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("sex",
             labeller = labeller(sex = c("female" = "Female proportion "))) +
  geom_line(aes(color = period),
            alpha = 0.01) +
  geom_line(data = quantile_bootstrapped_fitted_sex[ quantile_bootstrapped_fitted_sex$sex =="female", ],
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$sex =="female" & quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patients_hospitalized_agg_sex_total[ patients_hospitalized_agg_sex_total$sex =="female",],
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  #scale_colour_manual(values = wesanderson::wes_palette("GrandBudapest1", 3)) +
  scale_colour_manual(values = cbPalette) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = 6)+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  scale_colour_manual(values = cbPalette, labels = c("pre-pandemic", "pandemic"), name = "Period") +
  geom_label(data = plot_annotations_sex_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10),
         panel.grid.minor.x = element_blank(), 
        panel.grid.minor.y = element_blank(),
        title = element_text(size = 14), 
        plot.subtitle = element_text(size = 12, face = "italic"),
        legend.position = "bottom") 
ggsave("figure4_boostrapped_sex.png", height = 15, width = 20, units = "cm")
```

>>>>

ci_boot <- bootstrapped_coefficients_all %>% 
  group_by(siteid, term) %>% 
  summarise("2.5%" = quantile(bootstrapped_slope_coefficient, 0.025), 
            "50%" = quantile(bootstrapped_slope_coefficient, 0.50), 
            "97.5%" = quantile(bootstrapped_slope_coefficient, 0.975)) %>% 
  mutate(ci = paste0("(95% CI ", as.character(format(round(`2.5%`, 2)), nsmall =2), "–", as.character(format(round(`97.5%`, 2)), nsmall=2), ")"))

@@

```{r}
pvalues_boot_complete <- pvalues_boot %>% 
  inner_join(ci_boot) %>% 
  inner_join(country_map) %>% 
  arrange(plotsLabel) %>% 
  #mutate(string = paste0(observed_slope_coefficient, "% ", ci, " (p-value ", format.pval(pvalue, digits = 3, eps = 10**-2), ")")) %>%
  mutate(string = paste0(observed_slope_coefficient, "% ", ci)) %>%
  select(plotsLabel, string) %>% 
  pivot_wider(names_from = term, values_from = string) %>% 
  select(plotsLabel, before_slope, during_slope, difference_slope) %>% 
  rename("Before pandemic trend [95% CI] (p-value)" = before_slope,
        "Since pandemic trend [95% CI] (p-value)" = during_slope,
        "Difference before/since pandemic trend [95% CI] (p-value)" = difference_slope)

@@

```{r}
bootstrapped_fitted_all %>%
  mutate( time_p = as.character(time_p),
                  time_p = if_else(time_p == '2020-03-01', as.character('2020-03-15'), time_p),
                  time_p = if_else(time_p == '2020-04-01', as.character('2020-03-16'), time_p),
                  time_p = as.Date(time_p)) %>%
  ggplot(aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_all,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = 6)+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  scale_colour_manual(values = cbPalette, labels = c("pre-pandemic", "pandemic"), name = "Period") +
  geom_label(data = plot_annotations_df_primary, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(
    #title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
    #subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 14),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        panel.grid.minor.x = element_blank(), 
        panel.grid.minor.y = element_blank(),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic"), 
        legend.position="bottom")

@@

bootstrapped_fitted_sex %>% 
  filter( sex == "female") %>%
  mutate(period = recode_factor(period, "before_pandemic" = "Before pandemic onset", "during_pandemic" = "Since pandemic onset"), 
                  time_p = as.character(time_p),
                  time_p = if_else(time_p == '2020-03-01', as.character('2020-03-15'), time_p),
                  time_p = if_else(time_p == '2020-04-01', as.character('2020-03-16'), time_p),
                  time_p = as.Date(time_p)) %>% 
  ggplot(aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("sex",
             labeller = labeller(sex = c("female" = "Female proportion "))) +
  geom_line(aes(color = period),
            alpha = 0.01) +
  geom_line(data = quantile_bootstrapped_fitted_sex[ quantile_bootstrapped_fitted_sex$sex =="female", ],
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$sex =="female" & quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patients_hospitalized_agg_sex_total[ patients_hospitalized_agg_sex_total$sex =="female",],
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  #scale_colour_manual(values = wesanderson::wes_palette("GrandBudapest1", 3)) +
  scale_colour_manual(values = cbPalette) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = 6)+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  scale_colour_manual(values = cbPalette, labels = c("pre-pandemic", "pandemic"), name = "Period") +
  geom_label(data = plot_annotations_sex_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10),
         panel.grid.minor.x = element_blank(), 
        panel.grid.minor.y = element_blank(),
        title = element_text(size = 14), 
        plot.subtitle = element_text(size = 12, face = "italic"),
        legend.position = "bottom") 
ggsave("figure4_boostrapped_sex.png", height = 15, width = 20, units = "cm")
```
